Extracting sunbeams from cucumbers: Computational reproducibility is essential for archaeological science

### 2025-02-11 analysis/paper/paper.qmd
simplify structure and add readme

items_df <- read_rds("data/wos-data-df.rds")

@@

```{r}
# reporting on my AER work
jas_rr_data <- read_csv("data/JAS AER data analysis.csv")
base_size <- 10

>>>>

items_df <- 
  read_rds(here::here("analysis/data/wos-data-df.rds"))

@@

```{r}
# reporting on my AER work
jas_rr_data <- 
  read_csv(here::here("analysis/data/JAS AER data analysis.csv"))

base_size <- 10
